Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Say "Figure"

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S (see ~\ref{fig:scantegrity}).

>>>>

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).
